Tidal Locking in Low-Mass Stellar Binary Stars

### 2018-11-12 Paper/sync.tex
Updates from ShareLaTeX

-tidally locking before 5 Gyr occurs for most binaries below orbital periods of 60-70 days regardless of tidal parameter

-compute cumulative fraction of tidal-locking times in Porb bins plot so I can say x fraction are stars with Porb $< 60$d are tidally locked.

-make locking.py plot from previous paper with new data

@@

- Lurie has some binaries with Porb/Prot = 0.9, subsynchronous rotators.  cite his explaination for them

@@

@@

\begin{figure}[t]
	\includegraphics[width=\textwidth]{../Plots/lurieFig7.pdf}
   \caption{Caption}%
    \label{fig:lurie7}%
\end{figure}

@@

\begin{figure}
	\includegraphics[width=0.45\textwidth]{../Plots/subsyncTauHist.pdf}
   \caption{Caption}%
    \label{fig:subsyncTauHist}%
\end{figure}

>>>>

@@

@@

- cite Matsen+2018 for "more than $50\%$ of thebinary period distribution will be imaged in about $85\%$ of the host stars" in paper
about detecting unresolved binaries in TESS

@@

\begin{figure*}[t]
	\includegraphics[width=\textwidth]{../Plots/lurieFig7.pdf}
   \caption{Caption}%
    \label{fig:lurie7}%
\end{figure*}

@@
